### 2013-02-01 analysis/SandboxMax/20052007SalesData_Interaction.Rmd
2/1/2013

library (foreign)
workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20082010.dbf")
require(zoo)
require(lmtest)
require(car)

@@

Now we include interaction terms to view if there is an interaction effect between distance to the CBD and (1) Land Size and (2) Traffic Noise. Note that all quadratic relationships and interaction terms are significant.

```{r}
model.SaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + log(MAX) * CBD_dist + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

@@

Since all interaction terms were significant, we include more interaction terms that resemble the nonlinear relationship land size and distance to the central business district have with logged sales value. Note that the inclusion of more interaction terms that reflect the nonlinear relationship makes all interactions non-significant, perhaps multicollinearity is present.

```{r}
model.SaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + ACRES_POLY*I(CBD_dist^2)+I(ACRES_POLY^2)*I(CBD_dist^2)+ I(ACRES_POLY^2)*CBD_dist + log(MAX) * CBD_dist +log(MAX)*I(CBD_dist^2) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue4)
```

The last model keeps the interaction terms as well as Acres * CBD^2, which was closest to signficance level in the preceding model. We see that all interaction terms are significant. These coefficients suggest that the value of land increases as a parcel is closer to the central business district, at a decreasing rate. Also, the value of traffic noise disturbance increases as a parcel get farther away from the central business district.

```{r}
model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)+ACRES_POLY*I(CBD_dist^2)+ log(MAX) * CBD_dist +  HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue5)
```

>>>>

library (foreign)
workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052007.dbf")
require(zoo)
require(lmtest)
require(car)

@@

Now we include interaction terms to view if there is an interaction effect between distance to the CBD and (1) Land Size and (2) Traffic Noise. Note that all non linear relationships are significant except for CBD distance. Also, both interaction effects are insignificant however I believe that getting rid of the insignificant quadratic term for CBD will yield significant results for the interaction between land size and location.

```{r}
model.SaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist +I(CBD_dist^2)+I(ACRES_POLY^2)+ log(MAX) * CBD_dist + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

@@

Excluding the quadratic term for CBD distance and the interaction effect between traffic noise and CBD distance did not make the interaction effect between land size and distance significant.
```{r}
model.SaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist+I(ACRES_POLY^2)+ log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue4)

Including all possible interaction effects between land size and distance to CBD yields significant results.
```{r}
model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2) * CBD_dist + I(ACRES_POLY^2) * I(CBD_dist^2)+ ACRES_POLY * I(CBD_dist^2)+log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue5)
